Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-01 Paper/RSVOptimization.rnw
Don’t show bajillion splines

    data = tollandPredFull

    ggplot(data) +
      theme_light(base_size=plotTextBaseSize) +
      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
      geom_violinh(
        data=tollandOnsetFull,
        aes(x=onset, y=seasonThreshold),
        width=.01,
        fill="gray50", color="black",
        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
      ) +
      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
      scale_y_continuous() +
      coord_cartesian(xlim=c(zoomedStartWeek, zoomedEndWeek), ylim=c(0, 4*seasonThreshold)) +
      theme(
        panel.grid.major.x=element_blank(),
        legend.title=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
        legend.position="bottom"
      )
    dev.off()
@

\begin{figure}
\begin{center}
\input{\figuresDir/tollandOnsetFull}
\caption{Distribution of approximating $P$-splines and the calculated season onset with $N=\Sexpr{simulations}$ samples, for cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut.}
\label{fig:tollandOnsetFull}
\end{center}
\end{figure}

>>>>

    data = tollandPredFull
    splineData = data %>% filter(sim < tollandDisplayNsim)

    ggplot(data) +
      theme_light(base_size=plotTextBaseSize) +
      geom_line(data=splineData, aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
      geom_violinh(
        data=tollandOnsetFull,
        aes(x=onset, y=seasonThreshold),
        width=.01,
        fill="gray50", color="black",
        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
      ) +
      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
      scale_y_continuous() +
      coord_cartesian(xlim=c(zoomedStartWeek, zoomedEndWeek), ylim=c(0, 4*seasonThreshold)) +
      theme(
        panel.grid.major.x=element_blank(),
        legend.title=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
        legend.position="bottom"
      )

\begin{figure}
\begin{center}
\input{\figuresDir/tollandOnsetFull}
\caption{Distribution of approximating $P$-splines ($N=\Sexpr{tollandDisplayNsim}$) and season onset ($N=\Sexpr{tollandNsimFull}$), for cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut.}
\label{fig:tollandOnsetFull}
\end{center}
\end{figure}
